final_project_draft

### 2022-04-20 draft.Rmd
April 20th graded before class commit. Kept modifying components of theme for visualizations and worked on making a few more.

ggplot(data = high_donations, aes(x = amount, y = owner_ordered, label = Recipient, colour = party)) +
  geom_point(size = 2) +
  labs(x = " ", 
       y = " ",
       title = "How Much Did NFL Owners Donate in 2016?",
       colour = "Political Party",
       subtitle = "What Influence Could NFL Team Owners Have on Elections?") +
  scale_colour_viridis_d() +
  theme_bw() +
  theme(plot.title = element_text(family = "mono",
                                  face = "bold",
                                  size = 15,
                                  margin = margin(c(t = 20,
                                                    b = 50,
                                                    vjust = 10))),
        plot.subtitle = element_text(family = "mono",
                                     face = "italic",
                                     size = 10),
        legend.title = element_text(family = "mono",
                                    face = "bold",
                                    size = 8),
        legend.text = element_text(family = "mono",
                                   size = 8),
        axis.text = element_text(family = "mono",
                                 size = 8),
        legend.box.background = element_rect(),
        legend.position = "bottom") 
```

@@

ggplot(data = frequent, aes(x = amount, y = level_order, label = Amount, colour = Party)) +
  geom_point() +
  labs(title = "How Many Donations Have They Made?",
       subtitle = "Examining The Monetary Amount of Observed Political Donations",
       y = " ",
       x = " ",
       colour = "Party") +
  scale_colour_brewer(palette = "Dark2") +
    theme_bw() +
  theme(legend.position = "bottom",
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  size = 12),
        axis.text.x = element_text(family = "mono"),
        axis.text.y = element_text(family = "mono"),
        legend.title = element_text(family = "mono", 
                                    face = "bold",
                                    size = 5),
        legend.text = element_text(family = "mono",
                                   size = 5),
        plot.subtitle = element_text(family = "mono",
                                     face = "italic",
                                     size = 9),
        legend.box.background = element_rect())
```

@@

ggplot(data = cj_party, aes(x = party, y = n, fill = Party)) +
  geom_col() +
  coord_flip() +
  scale_fill_brewer(palette= "Pastel2") +
  labs(title = "Party Affiliation of Political Donations Made by Charles Johnson",
       x = " ",
       y = " ") +
  theme(legend.position = "bottom",
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  hjust = 0.5,
                                  size = 13,
                                  margin = margin(c(t = 50,
                                                    b = 50)),
                                  vjust = 10),
        axis.text = element_text(family = "mono"),
        legend.title = element_text(family = "mono",
                                    face = "bold"),
        legend.text = element_text(family = "mono"),
        axis.ticks.y = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_text(family = "mono",
                                    size = 9,
                                    face = "italic",
                                    margin = margin(t = 20)),
        axis.title.y = element_text(family = "mono",
                                    margin = margin(t = 20, b = 20, r = 20)))

@@

ggplot(data = recipients, aes(x = recipient, y = n, fill = Party)) +
  geom_col() +
  coord_flip() +
  labs(x = " ",
       y = "Count of Donations") +
  labs(title = "Organizations Receiving Most Donations Among All Owners") +
  scale_fill_brewer(palette = "Accent") +
  theme(legend.position = "bottom") +
  scale_x_discrete(labels = new_names) +
  theme(plot.title = element_text(family = "mono",
                                  face = "bold",
                                  margin = margin(c(t = 50,
                                                    b = 50)),
                                  vjust = 7),
        axis.text = element_text(family = "mono"),
        axis.title = element_text(family = "mono",
                                  size = 8),
        axis.title.x = element_text(size = 10,
                                    margin = margin(t = 10,
                                                    b = 10)),
        legend.title = element_text(family = "mono",
                                    face = "bold"),
        legend.text = element_text(family = "mono"),
        axis.ticks = element_blank(),
         legend.box.background = element_rect())

@@

ggplot(data = top10, aes(x = order, y = NetWorth, fill = Industry)) +
  geom_col() +
  coord_flip() +
  labs(x = "Billionaire", 
       y = "Net Worth",
       caption = "Measured in Billions",
       colour = "Industry",
       title = "2021 Forbes Billionaires with the Highest Net Worth") +
  scale_fill_viridis_d() +
  scale_x_discrete(labels = new_names2) +
  theme(legend.position = "bottom") +
  theme(axis.title = element_text(family = "mono",
                                  face = "bold",
                                  margin = margin(c(t = 30,
                                                    b = 30))),
        legend.box.spacing = unit(0.5, 'cm'),
        axis.text = element_text(family = "mono"),
        axis.ticks = element_blank(),
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  margin = margin(c(t = 15,
                                                    b = 15,
                                                    vjust = 15))),
        legend.margin = margin(c(t = 30)),
        legend.title = element_text(family = "mono",
                                    face = "bold"),
        legend.text = element_text(family = "mono",
                                   face = "italic"),
        plot.caption = element_text(family = "mono",
                                    face = "italic",
                                    vjust = 45,
                                    hjust = 0.5,
                                    margin = margin(c(t = 30,
                                                      b = 30))),
        legend.key.size = unit(.3, 'cm'))
```

@@

filter <- countries_10 %>% filter(!is.na(age))
filter
filter2 <- filter %>% group_by(Country) %>%
  summarise(Average = mean(age)) %>%
  mutate(order = fct_reorder(.f = Country, .x = Average))
filter3 <- filter2 %>% rename(age = 'Average')
```

## Outliers labeled 
```{r}
ggplot(data = countries_10, aes(x = Country, y = age)) +
  geom_point(alpha = 0.4) +
  coord_flip() +
  geom_point(data = filter2, aes(x = order, y = Average, colour = "Mean Age of Billionaires"),
             size = 2.5) +
  scale_colour_manual(values = c("Mean Age of Billionaires" = "red")) +
  labs(x = "Country", 
       y = "Age",
       title = "Average Age of Billionaires by Country") +
  theme(legend.position = "bottom") +
  theme(axis.title = element_text(family = "mono",
                                  face = "bold"),
        axis.text = element_text(family = "mono"),
        plot.title = element_text(family = "mono",
                                  face = "bold"),
        axis.ticks = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(family = "mono",
                                   face = "italic"), 
        plot.caption = element_text(family = "mono",
                                    size = 9,
                                    face = "italic")) 
```

@@

ggplot(data = above_or_below_us, aes(x = order, y = networth, colour = above_avg)) +
  geom_segment(aes(x = order, xend = order, y = avg, yend = networth)) +
  geom_point() +
  coord_flip() +
  labs(x = "Name",
      y = "Net Worth",
      caption = "Measured in Billions",
      colour = "Average",
      title = "Billionaires In The Fashion Industry",
      subtitle = "Do these billionaires fall above or below the average billionaire net worth in the U.S.?") +
  theme(axis.text = element_text(family = "mono"),
        axis.title = element_text(family = "mono"),
        legend.text = element_text(family = "mono"),
        legend.title = element_text(family = "mono"),
        plot.caption = element_text(family = "mono",
                                    hjust = 0.5),
        plot.title = element_text(family = "mono"),
        plot.subtitle = element_text(family = "mono"),
        axis.ticks = element_blank())
```

@@

ggplot(data = country_30, aes(x = order, y = n)) +
  geom_point(colour = "orange") +
  geom_segment(aes(x = order, xend = order, y = 0, yend = n), colour = "blue", linetype = "dotdash") +
  coord_flip() +
  theme_light() +
  theme(axis.ticks.x = element_blank()) +
  labs(x = "Country", 
       y = "Count of Billionaires",
       title = "How Many Billionaires Are There From the Top 30 Countries?") +
  theme(plot.title = element_text(family = "mono"),
        axis.text = element_text(family = "mono"),
        axis.title = element_text(family = "mono"))
```

## Playing Around with New Variables - looking at self made billionaires, education level of billionaires 
```{r}
self_made <- forbes_billionaires %>% group_by(Self_made) %>%
  summarise(n = n())

ggplot(data = forbes_billionaires, aes(x = Self_made)) +
  geom_bar()

industry <- billionaires %>% group_by(Industry) %>%
  summarise(n = n()) %>%
  arrange(desc(n))
industry

combined_billionaires <- left_join(forbes_billionaires, billionaires, by = c("Name" = "Name"))
combined_billionaires

@@

harvard <- tidy_education %>% filter(University == "Harvard University")
harvard

tidy_education2 <- tidy_education %>% filter(Degree == "Bachelor of Arts/Science" |
                          Degree == "Master of Business Administration" |
                          Degree == "Master of Science" |
                          Degree == "Drop Out" |
                          Degree == "Bachelor of Science" |
                          Degree == "Bachelor of Science in Engineering" |
                          Degree == "Doctorate" |
                          Degree == "Diploma" |
                          Degree == "Bachelor of Arts/Economic")

@@

## Forbes Billionaire 2021 3.0 Data Set 
```{r}
forbes_billionaires_geo <- read_csv("data/forbes_billionaires_geo.csv")
forbes_billionaires_geo 
```

>>>>

ggplot(data = high_donations, aes(x = amount, y = owner_ordered, label = Recipient, colour = party)) +
  geom_point(size = 2) +
  labs(x = " ", 
       y = " ",
       title = "How Much Did NFL Owners Donate in 2016?",
       colour = "Political Party",
       subtitle = "What Influence Could NFL Team Owners Have on Elections?") +
  scale_colour_viridis_d() +
  theme_bw() +
  theme(plot.title = element_text(family = "mono",
                                  face = "bold",
                                  size = 15,
                                  margin = margin(c(t = 20,
                                                    b = 50,
                                                    vjust = 10))),
        plot.subtitle = element_text(family = "mono",
                                     face = "italic",
                                     size = 10),
        legend.title = element_text(family = "mono",
                                    face = "bold",
                                    size = 8),
        legend.text = element_text(family = "mono",
                                   size = 8),
        axis.text = element_text(family = "mono",
                                 size = 8),
        axis.text.x = element_text(face = "bold"),
        legend.box.background = element_rect(),
        axis.ticks = element_blank(),
        legend.position = "bottom") 
```

@@

ggplot(data = frequent, aes(x = amount, y = level_order, label = Amount, colour = Party)) +
  geom_point() +
  labs(title = "How Many Donations Have They Made?",
       subtitle = "Examining The Monetary Amount of Observed Political Donations",
       y = " ",
       x = " ",
       colour = "Party") +
  scale_colour_brewer(palette = "Dark2") +
    theme_bw() +
  theme(legend.position = "bottom",
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  size = 12),
        axis.text.x = element_text(family = "mono"),
        axis.text.y = element_text(family = "mono"),
        legend.title = element_text(family = "mono", 
                                    face = "bold",
                                    size = 8),
        legend.text = element_text(family = "mono",
                                   size = 8),
        plot.subtitle = element_text(family = "mono",
                                     face = "italic",
                                     size = 9),
        axis.ticks = element_blank(),
        legend.box.background = element_rect())
```

@@

ggplot(data = cj_party, aes(x = party, y = n, fill = Party)) +
  geom_col(colour = "black") +
  coord_flip() +
  scale_fill_brewer(palette= "Pastel2") +
  labs(title = "Party Affiliation of Political Donations Made by Charles Johnson",
       x = " ",
       y = " ") +
  theme(legend.position = "bottom",
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  hjust = 0.5,
                                  size = 13,
                                  margin = margin(c(t = 50,
                                                    b = 50)),
                                  vjust = 10),
        axis.text = element_text(family = "mono"),
        legend.title = element_text(family = "mono",
                                    face = "bold"),
        legend.text = element_text(family = "mono"),
        axis.ticks.y = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_text(family = "mono",
                                    size = 9,
                                    face = "italic",
                                    margin = margin(t = 20)),
        axis.title.y = element_text(family = "mono",
                                    margin = margin(t = 20, b = 20, r = 20)))

@@

ggplot(data = recipients, aes(x = recipient, y = n, fill = Party)) +
  geom_col(colour = "black") +
  coord_flip() +
  labs(x = " ",
       y = "Count of Donations") +
  labs(title = "Organizations Receiving Most Donations Among All Owners") +
  scale_fill_brewer(palette = "Accent") +
  theme(legend.position = "bottom") +
  scale_x_discrete(labels = new_names) +
  theme(plot.title = element_text(family = "mono",
                                  face = "bold",
                                  margin = margin(c(t = 50,
                                                    b = 50)),
                                  vjust = 7),
        axis.text = element_text(family = "mono"),
        axis.title = element_text(family = "mono",
                                  size = 8),
        axis.title.x = element_text(size = 10,
                                    margin = margin(t = 10,
                                                    b = 10)),
        legend.title = element_text(family = "mono",
                                    face = "bold"),
        legend.text = element_text(family = "mono"),
        axis.ticks = element_blank(),
         legend.box.background = element_rect())

@@

ggplot(data = top10, aes(x = order, y = NetWorth, fill = Industry)) +
  geom_col(colour = "black") +
  coord_flip() +
  labs(x = " ", 
       y = "Net Worth",
       caption = "Measured in Billions",
       colour = "Industry",
       title = "2021 Forbes Billionaires with the Highest Net Worth") +
  scale_fill_viridis_d() +
  scale_x_discrete(labels = new_names2) +
  theme(legend.position = "bottom") +
  theme(axis.title = element_text(family = "mono",
                                  face = "bold",
                                  margin = margin(c(t = 30,
                                                    b = 30))),
        axis.text = element_text(family = "mono"),
        axis.text.y = element_text(face = "bold"),
        axis.ticks = element_blank(),
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  margin = margin(c(t = 15,
                                                    b = 15,
                                                    vjust = 15))),
        axis.title.x = element_text(vjust = -3),
        axis.title.y = element_text(vjust = 2),
        legend.margin = margin(c(t = 30, b = 30)),
        legend.title = element_text(family = "mono",
                                    face = "bold"),
        legend.text = element_text(family = "mono",
                                   face = "italic"),
        plot.caption = element_text(family = "mono",
                                    face = "italic",
                                    vjust = 35,
                                    hjust = 0.5,
                                    margin = margin(c(t = 30,
                                                      b = 30))),
        legend.key.size = unit(.3, 'cm'))
```

@@

filter <- countries_10 %>% filter(!is.na(age))
filter
filter2 <- filter %>% group_by(Country) %>%
  summarise(Average = mean(age)) %>%
  mutate(order = fct_reorder(.f = Country, .x = Average))
filter3 <- filter2 %>% rename(age = 'Average')

ggplot(data = countries_10, aes(x = Country, y = age)) +
  geom_point(alpha = 0.4) +
  coord_flip() +
  geom_point(data = filter2, aes(x = order, y = Average, colour = "Mean Age of Billionaires"),
             size = 2.5) +
  scale_colour_manual(values = c("Mean Age of Billionaires" = "red")) +
  labs(x = "Country", 
       y = "Age",
       title = "Average Age of Billionaires by Country") +
  theme(legend.position = "bottom") +
  theme(axis.title = element_text(family = "mono",
                                  face = "bold"),
        axis.text = element_text(family = "mono"),
        plot.title = element_text(family = "mono",
                                  face = "bold"),
        axis.ticks = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(family = "mono",
                                   face = "italic"), 
        plot.caption = element_text(family = "mono",
                                    size = 9,
                                    face = "italic")) 
```

## Outliers labeled 
```{r}
ggplot(data = countries_10, aes(x = Country, y = age)) +
  geom_point(alpha = 0.4) +
  coord_flip() +
  geom_point(data = filter2, aes(x = order, y = Average, colour = "Mean Age of Billionaires"),
             size = 2.5) +
  scale_colour_manual(values = c("Mean Age of Billionaires" = "red")) +
  labs(x = "Country", 
       y = "Age",
       title = "Average Age of Billionaires by Country") +
  theme(legend.position = "bottom") +
  theme(axis.title = element_text(family = "mono",
                                  face = "bold"),
        axis.text = element_text(family = "mono"),
        plot.title = element_text(family = "mono",
                                  face = "bold"),
        axis.ticks = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(family = "mono",
                                   face = "italic"), 
        plot.caption = element_text(family = "mono",
                                    size = 9,
                                    face = "italic")) +
  geom_label_repel(data = check, aes(label = age))
```

@@

ggplot(data = above_or_below_us, aes(x = order, y = networth, colour = above_avg)) +
  geom_segment(aes(x = order, xend = order, y = avg, yend = networth)) +
  geom_point() +
  scale_colour_brewer(palette = "Accent") +
  coord_flip() +
  labs(x = " ",
      y = "Net Worth",
      caption = "Measured in Billions",
      colour = "Average",
      title = "Billionaires In The Fashion Industry",
      subtitle = "Do these billionaires fall above or below the average billionaire net worth in the U.S.?") +
  theme(axis.text = element_text(family = "mono"),
        axis.title = element_text(family = "mono"),
        legend.text = element_text(family = "mono"),
        legend.title = element_text(family = "mono",
                                    face = "bold"),
        plot.caption = element_text(family = "mono",
                                    hjust = 0.5),
        plot.title = element_text(family = "mono",
                                  face = "bold"),
        plot.subtitle = element_text(family = "mono",
                                     face = "italic"),
        axis.title.x = element_text(face = "bold"),
        axis.text.y = element_text(face = "italic",
                                   vjust = 1),
        axis.ticks = element_blank(),
        legend.box.background = element_rect()) 
```

@@

ggplot(data = country_30, aes(x = order, y = n)) +
  geom_point(colour = "orange") +
  geom_segment(aes(x = order, xend = order, y = 0, yend = n), colour = "blue", linetype = "dotdash") +
  coord_flip() +
  theme_light() +
  theme(axis.ticks.x = element_blank()) +
  labs(x = "Country", 
       y = "Count of Billionaires",
       title = "How Many Billionaires Are There From the Top 30 Countries?") +
  theme(plot.title = element_text(family = "mono"),
        axis.text = element_text(family = "mono"),
        axis.title = element_text(family = "mono"))

ggplot(data = country_30, aes(x = order, y = n, fill = n)) +
  geom_col(colour = "black") +
  coord_flip() +
  labs(x = " ", 
       y = " ",
       title = "How Many Billionaires Are There From the Top 30 Countries?",
       fill = "Count") +
  theme(plot.title = element_text(family = "mono",
                                  face = "bold"),
        axis.text = element_text(family = "mono"),
        axis.title = element_text(family = "mono"),
        legend.title = element_text(family = "mono",
                                    face = "bold"),
        legend.text = element_text(family = "mono",
                                   face = "italic"),
        axis.ticks = element_blank()) +
  scale_fill_viridis_b(n.breaks = 7) 
```

## Playing Around with New Variables - looking at self made billionaires, education level of billionaires 
```{r}
forbes_billionaires %>% select(Self_made, everything())
self_made <- forbes_billionaires %>% group_by(Self_made) %>%
  summarise(n = n()) %>%
  filter(!is.na(Self_made))

ggplot(data = self_made, aes(x = Self_made, y = n, fill = Self_made)) +
  geom_col(colour = "black") +
  scale_fill_brewer(palette = "Spectral") +
  labs(x = " ",
       y = " ",
       title = "How Many of These Billionaires Are Self-Made?",
       fill = " ") +
  theme(plot.title = element_text(family = "mono",
                                  face = "bold",
                                  margin = margin(c(t = 30)),
                                  vjust = 8,
                                  size = 15),
        legend.text = element_text(family = "mono"),
        axis.text = element_text(family = "mono"),
        axis.text.x = element_text(size = 15,
                                   face = "bold"),
        axis.ticks = element_blank(),
        axis.text.y = element_blank(),
        legend.position = "none") +
  geom_label(data = self_made, aes(label = n),
              fill = "white",
             label.size = 0.5) 
```

## Continuing to mess around 
```{r}
industry <- billionaires %>% group_by(Industry) %>%
  summarise(n = n()) %>%
  arrange(desc(n))
industry

combined_billionaires <- left_join(forbes_billionaires, billionaires, by = c("Name" = "Name"))

combined_billionaires2 <- combined_billionaires %>% separate(col = Education, into = c("Degree", "University"),
                                 sep = ", ")

harvard <- combined_billionaires2 %>% filter(University == "Harvard University") 
harvard

harvard %>% group_by(Industry) %>%
  summarise(n = n()) %>%
  arrange(desc(n))

ggplot(data = harvard, aes(x = Degree, y = NetWorth.x)) +
  geom_point() +
  coord_flip() +
  geom_label(data = harvard, aes(label = Name))

@@

tidy_education %>% filter(University == "Harvard University")
```

```{r}
tidy_education2 <- tidy_education %>% filter(Degree == "Bachelor of Arts/Science" |
                          Degree == "Master of Business Administration" |
                          Degree == "Master of Science" |
                          Degree == "Drop Out" |
                          Degree == "Bachelor of Science" |
                          Degree == "Bachelor of Science in Engineering" |
                          Degree == "Doctorate" |
                          Degree == "Diploma" |
                          Degree == "Bachelor of Arts/Economic")

@@

## New Data Set
```{r}

```
